Oral anticoagulants

### 2021-01-17 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Fixed error in calculating warfarin as a percentage of all oac within GP unit.

oac_p_monthly_quantity_gp <- 
  propRegional(oac, PracticeID, datename, Quantity, bnf = warf)

@@

oac_p_monthly_quantity_hb_pre_cv19 <- 
  oac_p_monthly_quantity_hb %>% 
    filter(datename < dmy("01-03-2020"))

oac_p_monthly_quantity_cluster_pre_cv19 <- 
  oac_p_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

@@

```{r, health-board-modelling}
plan(cluster)
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r}
plan(cluster)
system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_fcsts %>%
  write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
plan(cluster)
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

```{r}
plan(cluster)
system.time(oac_p_gp_cluster_fcsts <- 
              regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

```{r, gp-practice-modelling}
incomplete_gp <- # Need to remove GP Practices with incomplete data
  oac_p_monthly_quantity_gp_pre_cv19 %>% 
    as_tibble() %>% 
    group_by(regional_unit) %>% 
    count() %>% 
    filter(n < 50) %>% 
    .$regional_unit %>% 
    unique()

@@

# Running regionalCV() on each of the quarter of the data
plan(cluster)
system.time(oac_p_gp_cv_models_1 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
              regionalCV())
with_progress(system.time(oac_p_gp_cv_models_2 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
              regionalCV()))
system.time(oac_p_gp_cv_models_3 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_4 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
              regionalCV())
plan(sequential)

@@

```{r}
plan(cluster, workers = 8)
system.time(oac_p_gp_fcsts <-
              oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
plan(sequential)

@@

* 2020-12-18 2694 secs

@@

plan(cluster, workers = 8)
system.time(fable_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
plan(sequential)

joint_fcst <-
  bind_rows(fable_fcst, prophet_fcst) %>%
  mutate(lb_95 = quantile(n, .025),
         lb_80 = quantile(n, .1),
         med = median(n),
         ub_80 = quantile(n, .9),
         ub_95 = quantile(n, .975),
         sd = distributional::variance(n)^2,
         dist = n,
         n = NULL)
joint_fcst %>%
  saveRDS("../data/oac_p_gp_fcsts.rds")

@@

```{r, eval = FALSE}
best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = 1000000*(n - .mean), # Why are the numbers so small?
         regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  mutate(regional_unit = as.numeric(regional_unit)) %>% 
  na.omit() %>% .[2:5] %>% min()
  write_csv(file = "../data/mplus/oac_gp_discrep.csv", col_names = FALSE)
```

```{r, eval = FALSE}
source("../r_scripts/functions/mplus_plotting.R")
mplus.view.plots("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
mplus.plot.estimated_means("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
```

>>>>

oac_p_monthly_quantity_gp <- 
  oac %>% 
  group_by(PracticeID, datename, bnfchem) %>% 
  summarise(sum_n = sum(Quantity), .groups = "drop_last") %>% 
  mutate(p_war = 100 * sum_n / sum(sum_n)) %>% 
  filter(bnfchem == as_name(warf)) %>% 
  transmute(regional_unit = as.factor(PracticeID),
            datename = datename,
            n = p_war) %>%
    ungroup() %>%
    as_tsibble(index = datename, key = regional_unit)

@@

# oac_p_monthly_quantity_hb_pre_cv19 <- 
#   oac_p_monthly_quantity_hb %>% 
#     filter(datename < dmy("01-03-2020"))
# 
# oac_p_monthly_quantity_cluster_pre_cv19 <- 
#   oac_p_monthly_quantity_cluster %>% 
#     filter(datename < dmy("01-03-2020"))

@@

```{r, health-board-modelling, eval = FALSE}
plan(cluster)
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r health-board-forecast, eval = FALSE}
plan(cluster)
system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_fcsts %>%
  write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling, eval = FALSE}
plan(cluster)
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

```{r gp-cluste-forecast, eval = FALSE}
plan(cluster)
system.time(oac_p_gp_cluster_fcsts <- 
              regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

```{r, gp-practice-modelling}
incomplete_gp <- # Need to remove GP Practices with incomplete data
  oac_p_monthly_quantity_gp_pre_cv19 %>% 
  as_tibble() %>% 
  group_by(regional_unit) %>% 
  count() %>% 
  filter(n < 50) %>% 
  .$regional_unit %>% 
  as.character() %>% 
  unique()

@@

# Running regionalCV() on each of the quarter of the data
plan(multisession)
system.time(oac_p_gp_cv_models_1 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_2 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_3 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_4 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
              regionalCV())
plan(sequential)

@@

```{r gp-practice-forecast}
plan(multisession)
system.time(oac_p_gp_fcst_1 <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% seg_1) %>%
    regionalJointFcsts())
system.time(oac_p_gp_fcst_2 <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% seg_2) %>%
    regionalJointFcsts())
system.time(oac_p_gp_fcst_3 <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% seg_3) %>%
    regionalJointFcsts())
system.time(oac_p_gp_fcst_4 <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% seg_4) %>%
    regionalJointFcsts())
plan(sequential)

oac_p_gp_fcsts <-
  bind_rows(oac_p_gp_fcst_1,
            oac_p_gp_fcst_2,
            oac_p_gp_fcst_3,
            oac_p_gp_fcst_4)

@@

* NaNs producedNaNs producedfable forecasts complete
prophet forecasts complete
    user   system  elapsed 
  97.430   22.773 1580.689 
fable forecasts complete
prophet forecasts complete
    user   system  elapsed 
 106.565   84.755 1719.863 
fable forecasts complete
prophet forecasts complete
    user   system  elapsed 
 114.419  116.874 1867.420 
fable forecasts complete
prophet forecasts complete
    user   system  elapsed 
 113.032  124.767 1910.564

@@

plan(multisession)
system.time(fable_fit_1 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[1:101],
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit_1 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[1:101],
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
system.time(fable_fit_2 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[102:202],
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit_2 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[102:202],
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
system.time(fable_fit_3 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[203:303],
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit_3 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[203:303],
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
system.time(fable_fit_4 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[304:404],
                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                          regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())

system.time(prophet_fit_4 <-
  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[304:404],
                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                            regional_unit ==.x)),
                 .options = furrr_options(seed = TRUE)) %>%
  forecast(h = "5 months") %>%
  as_tibble())
plan(sequential)

joint_fcst <-
  bind_rows(fable_fcst_1, prophet_fcst_1,
            fable_fcst_2, prophet_fcst_2,
            fable_fcst_3, prophet_fcst_3,
            fable_fcst_4, prophet_fcst_4) %>%
  mutate(lb_95 = quantile(n, .025),
         lb_80 = quantile(n, .1),
         med = median(n),
         ub_80 = quantile(n, .9),
         ub_95 = quantile(n, .975),
         sd = distributional::variance(n)^2,
         dist = n,
         n = NULL)
joint_fcst %>%
  saveRDS("../data/oac_p_gp_fcsts.rds")

@@

```{r}
best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         # regional_unit = as.character(regional_unit)
         ) %>% 
  ggplot(aes(x = datename, y = n, group = regional_unit)) +
  geom_line() +
  facet_wrap(~regional_unit)

  as_tsibble(key = regional_unit, index = datename) %>% 
  autoplot(oac_p_monthly_quantity_gp_pre_cv19 %>% 
             select(regional_unit, datename, n) %>% 
             as_tsibble(key = regional_unit, index = datename)) +
  theme(legend.position = "none")
```
